Twisted 11-dimensional supergravity

### 2021-10-15 intro.tex
small typos

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}. (Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)

@@

\begin{table}[]
\begin{tabular}{c|c|c|c|c|c|c|c|}
\cline{2-7}
& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
\multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
\end{tabular}
\caption{A summary of twists of 10-dimensional supergravity}
\label{table:IIsugra}
\end{table}

>>>>

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lceil d/2\rceil$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}. (Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)

@@

\begin{table}[]
\begin{tabular}{c|c|c|c|c|c|c|c|}
\cline{2-7}
& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ &  & $\RR^{10}_A$  \\ \hline
\multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
\end{tabular}
\caption{A summary of twists of 10-dimensional supergravity}
\label{table:IIsugra}
\end{table}
